Optiplan proposal

### 2018-03-20 R/OptiPlan_presentation/proposal_fr.Rmd
Take tex generation out of compilation for pdf

---
title: "Optiplan proposal"
author: "ISAE-SUPAERO, Université de Toulouse"
date: "Mars 11, 2018"
nocite: '@*'
output:
  html_document:
    css: ./../../css/baobab_docs.css
    toc: yes
  beamer_presentation:
    pandoc_args: ["--slide-level=3", "--top-level-division=part"]
    # fig_height: 4
    # includes:
    #   in_header: header.tex
    # incremental: yes
    # slide_level: 3
    theme: Madrid
    # toc: yes
  pdf_document:
    toc: yes
    # toc_depth: 2
    # template: ./../../latex/templates/baobab.tex
    template: isae-report-template_pandoc.tex
    # top_level_division: part
    keep_tex: true
    pandoc_args: ["--top-level-division=part"]
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    footer: ISAE-SUPAERO, Université de Toulouse, France
    # incremental: yes
    slide_level: 3
    pandoc_args: ["--slide-level=3"]
    toc: yes
bibliography: MFMP.bib
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Optiplan proposal"
author: "ISAE-SUPAERO, Université de Toulouse"
date: "Mars 11, 2018"
nocite: '@*'
output:
  html_document:
    css: ./../../css/baobab_docs.css
    toc: yes
  beamer_presentation:
    pandoc_args: ["--slide-level=3", "--top-level-division=part"]
    # fig_height: 4
    # includes:
    #   in_header: header.tex
    # incremental: yes
    # slide_level: 3
    theme: Madrid
    # toc: yes
  pdf_document:
    toc: yes
    # toc_depth: 2
    # template: ./../../latex/templates/baobab.tex
    template: isae-report-template_pandoc.tex
    # top_level_division: part
    # keep_tex: true
    pandoc_args: ["--top-level-division=part"]
  slidy_presentation:
    css: ./../../css/baobab_MH.css
    footer: ISAE-SUPAERO, Université de Toulouse, France
    # incremental: yes
    slide_level: 3
    pandoc_args: ["--slide-level=3"]
    toc: yes
bibliography: MFMP.bib
editor_options: 
  chunk_output_type: console
---
